```{r setup,include=FALSE}
# set the knitr options ... for everyone!
# if you unset this, then vignette build bonks. oh, joy.
#opts_knit$set(progress=TRUE)
opts_knit$set(eval.after='fig.cap')
# for a package vignette, you do want to echo.
# opts_chunk$set(echo=FALSE,warning=FALSE,message=FALSE)
opts_chunk$set(warning=FALSE,message=FALSE)
#opts_chunk$set(results="asis")
opts_chunk$set(cache=TRUE,cache.path="cache/")

#opts_chunk$set(fig.path="figure/",dev=c("pdf","cairo_ps"))
opts_chunk$set(fig.path="figure/",dev=c("pdf"))
opts_chunk$set(fig.width=5,fig.height=4,dpi=64)

# doing this means that png files are made of figures;
# the savings is small, and it looks like shit:
#opts_chunk$set(fig.path="figure/",dev=c("png","pdf","cairo_ps"))
#opts_chunk$set(fig.width=4,fig.height=4)
# for figures? this is sweave-specific?
#opts_knit$set(eps=TRUE)

# this would be for figures:
#opts_chunk$set(out.width='.8\\textwidth')
# for text wrapping:
options(width=64,digits=2)
opts_chunk$set(size="small")
opts_chunk$set(tidy=TRUE,tidy.opts=list(width.cutoff=50,keep.blank.line=TRUE))

#SharpeR.meta <- packageDescription('SharpeR')
```

# SharpeR

A number of utilities for dealing with Sharpe ratio, the Sharpe ratio of the
Markowitz portfolio, and, in general, overfit of trading strategies based on
(in-sample) Sharpe statistics.

-- Steven E. Pav, shabbychef@gmail.com

## Installation

This package may be installed from CRAN; the latest version may be
found on [github](https://www.github.com/shabbychef/SharpeR "SharpeR")
via devtools:

```{r install,eval=FALSE,echo=TRUE}
if (require(devtools)) {
	# latest greatest
	install_github(repo='SharpeR',username='shabbychef',ref='master')
	# last release:
	install_github(repo='SharpeR',username='shabbychef',ref='r0.1309')
}
```

# Basic Usage

## using sr

```{r babysteps,eval=TRUE,echo=TRUE}
require(SharpeR)
# suppose you computed the Sharpe of your strategy to
# be 1.3 / sqrt(yr), based on 1200 daily observations.
# an object can be instanatiated as follows
my.sr <- sr(sr=1.3,df=1200-1,ope=252,epoch="yr")
print(my.sr)
```

And using real data:
```{r stock_loading,eval=TRUE,echo=TRUE}
require(quantmod)
options("getSymbols.warning4.0"=FALSE)

# get price data, compute log returns on adjusted closes
get.ret <- function(sym,warnings=FALSE,...) {
	# getSymbols.yahoo will barf sometimes; do a trycatch
  trynum <- 0
	while (!exists("OHCLV") && (trynum < 7)) {
		trynum <- trynum + 1
		try(OHLCV <- getSymbols(sym,auto.assign=FALSE,warnings=warnings,...),silent=TRUE)
  }
	adj.names <- paste(c(sym,"Adjusted"),collapse=".",sep="")
	if (adj.names %in% colnames(OHLCV)) {
		adj.close <- OHLCV[,adj.names]
	} else {
		# for DJIA from FRED, say. 
		adj.close <- OHLCV[,sym]
	}
	rm(OHLCV)
	# rename it
	colnames(adj.close) <- c(sym)
	adj.close <- adj.close[!is.na(adj.close)]
	lrets <- diff(log(adj.close))
	#chop first
	lrets[-1,]
}
get.rets <- function(syms,...) { some.rets <- do.call("cbind",lapply(syms,get.ret,...)) }
```


```{r real_data,eval=TRUE,echo=TRUE}
some.rets <- get.rets(c("IBM","AAPL","XOM"),
	from="2004-01-01",to="2013-08-01")
print(as.sr(some.rets))
```
